Effectful Semantics for Substructural SSA

### 2023-11-16 pldi24/paper.tex
Tap

\TODO{some text about what the semantics actually are...}

@@

>>>>

@@

We can now give a semantics for blocks in Figure \ref{fig:ssa-block-semantics}.
Our semantics for break statements \(\lbrb{\ell}{a}\) is given by the semantics
for splitting the context into variables which pass into dominated blocks and
variables used to compute the argument, \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\),
with the latter passed into the semantics of the argument (which is pure, and
therefore must be lifted to \(\mc{C}_0\))
\(\dnt{\hasty{\Gamma}{1}{a}{A}{\tint}}\), with the result along with the
preserved variables passed into \(\lwk{\llhyp{\ell}{\Delta}{A}}{\ms{L}}\) to
obtain the desired target. The semantics of if-statements are given by first
splitting the context via \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\) and then
calculating the discriminant \(\dnt{\hasty{\Delta}{1}{b}{\mb{2}}{\tint}}\),
which must be pure and therefore needs to be lifted. This is then passed through
the distributor \(\delta\), with each branch passed to the semantics of its
corresponding block \(\dnt{\haslb{\Xi}{s}{\ms{L}}}\),
\(\dnt{\haslb{\Xi}{t}{\ms{L}}}\).Tap
